---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## errum

<!-- badges: start -->
[![R-CMD-check](https://github.com/tmsalab/errum/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/tmsalab/errum/actions/workflows/R-CMD-check.yaml)
[![Package-License](http://img.shields.io/badge/license-GPL%20(%3E=2)-brightgreen.svg?style=flat)](https://www.gnu.org/licenses/old-licenses/gpl-2.0.html)
[![CRAN status](https://www.r-pkg.org/badges/version/errum)](https://CRAN.R-project.org/package=errum)
<!-- badges: end -->

Perform a Bayesian estimation of the Exploratory reduced Reparameterized Unified
Model ('ErRUM') described by Culpepper and Chen (2018).

### Installation

You can install `errum` from CRAN using:

```{r}
#| label: cran-installation
#| eval: false
install.packages("errum")
```

Or, you can be on the cutting-edge development version on GitHub using:

```{r}
#| label: gh-installation
#| eval: false
if(!requireNamespace("remotes")) install.packages("remotes")
remotes::install_github("tmsalab/errum")
```

### Usage

To use the `errum` package, load it into _R_ using:

```{r}
#| label: library-load
#| message: false
library("errum")
```

From there, the errum model can be estimated using:

```{r}
#| label: errum-est
#| eval: false
errum_model = errum(<data>, <k>, chain_length = 10000)
```

### Authors

James Joseph Balamuta, Steven Andrew Culpepper, and Jeffrey A. Douglas

### Citing the errum package

To ensure future development of the package, please cite `errum`
package if used during an analysis or simulation studies. Citation information
for the package may be acquired by using in *R*:

```{r}
#| label: citation
#| eval: false
citation("errum")
```

### License

GPL (>= 2)
